\section{Team Development}

The length and depth of this project allowed us to learn a great many things,
consisting of new technologies and new work methodologies. Key to this is the
agile workflow, which was required for this project. We all learnt how using
agile methods can be better for quick prototyping and helping to focus our
project early through frequent refinement. This was also necessary when our
requirements changed throughout the project, which would've meant extensive
rework if we weren't using agile.

Some of the technologies new to us was the Unity game engine, which was required
to use for the racing simulation. Only one group member had previously used this
before, which helped a great deal with the initial work but other group members
had to learn the framework and its intricacies. 

We also had to learn Node.js and the Express framework, which made us deal with
a lot of asynchronous javascript callbacks, and the model view controller design
pattern. Whilst we have encountered some of this before, we now feel more
comfortable in this environment, and also how it links together with Unity,
since the website had to send commands to our Unity game and vice versa.

Working with MongoDB instead of an SQL database is also different, since we no
longer have relational databases and store most things in the same collection;
we managed to learn a bit more about the structure of NoSQL databases and how you
have to use them in a certain way that differs from what we are used to.

\section{Project Reflections/Improvements}
% Some of this feels more like evaluation than reflecting back, although I
% guess it could be both - perhaps consider shuffling things around?

We feel that a lot of our initial project work went well, with a protoype
quickly forming and features being organised quickly. Looking back now, it is
easy to judge the tasks that will be more important that we could've worked on
from the start, especially since G-Research have pointed out more of what they
want as the project went on. Most of what we did went well and worked for us, so
we wouldn't want to change how we worked drastically, but there were a few key
issues that would've resulted in fewer problems for us later.

One of these problems was with deploying the Unity side of the game. The
compiled web build had to be made with the Unity editor, and so was included in
the git repository as this is what was transferred to the VM our project ran on.
This web build was very large, and resulted in significantly long build times,
as well as causing us problems with disk space on the VM, since git would keep
all previous versions of it as part of its history. Towards the end of the
project, we found that there were ways of removing this build from previous
commits, which would help with our disk space problems. We also managed to find
a command line version of Unity that could compile the web build on the VM,
although this would have to run on Windows, whether through another virtual
machine or just having the one we used as Windows instead of Linux. We didn't
change this around as we had almost finished, and it could potentially break our
project at an important time if we tried to alter this too much. However, this
would be something we would strongly consider doing were we to do it again,
since it would solve a vast amount of the annoyances we encountered above.

Another problem was using the MongoDB database, although mostly at our own
fault. We made some initial collections that we thought would be separate, but
found later that we needed to 'join' them. However, this cannot be done easily
with NoSQL, and eventually we created a new collection to house all the data. We
felt slighly uncomfortable using something that didn't have relational data, and
never really got used to the paradigm shift, so perhaps using a relational model
would've sped up our working and avoided these problems. At the same time, it is
good to know about NoSQL databases, and we would not have learnt about it during
this project otherwise, so we would need to consider which tradeoffs are worth
it.

Whilst we tried to adhere to agile methods when working on this project, we
found that we didn't do everything we could have done. Scrums weren't
consistent, mainly because we worked together in the same place and it wasn't as
necessary to always stop working and discuss working - instead they happened
only when absolutely necessary (i.e. when designing a new feature). We also
didn't rotate our team members a lot. Using more agile methods would've taught
us a lot more about this way of working, as well as potentially improving the
work we do.

Our sprints were two weeks long, which seemed to work well due to the other work
we had to complete in the timeframe (coursework and such), but more feedback
more frequently is always better, so perhaps shortening this would've improved
our work.

\section{Future Extensions}
% There can probably be a lot for this... list the key features we would
% want to add, or the ones we were planning on adding before we ran out of time

Whilst we got the key features completed on time, there are a few things we were 
thinking about doing towards the end of the project that we could do if we had
more time to work on it. G-Research have mentioned that this project could
potentially be continued by another university, so these extensions could
eventually form a specification for them to work on.

Below is a list of the extensions ideas we have and the reasons for them:

\begin{itemize}
    \item
        \textbf{More Extensive API} - Allowing more control over the car allows
        for more complex and detailed AI scripts, and could help find the best
        candidates who can use all the features. Examples of this include 
    \item
        \textbf{Better car physics} - Our simulated car physics could do with
        some improvements - for example when moving backwards the car has a
        tendency to flip over for no reason. The brake system also doesn't work
        that well with the road, meaning a negative throttle is more effective
        at stopping than braking is.
    \item
        \textbf{Cleaner setup} - Currently our deployment system consists of
        downloading the Github repository, and making sure to install the
        prerequisites (MongoDB and Node), then running the web server. This
        could be packaged up into an installer that bundles the compiled code
        and the prerequisites together for easy installation.
    \item
        \textbf{Better security} - We don't have much security for our project,
        mainly because it was only required to run at a careers fair in a closed
        network, which wouldn't be vulnerable anyway. However, those with
        knowledge of the source code could potentially use it to their advantage
        and modify the rules of the simulation, allowing them to perform better.
    \item
        \textbf{Better documentation} - More extensive documentation along with
        some example scripts on how to use the API would definitely aid future
        users with how best to go about writing a racing AI.
    \item
        \textbf{Improving other scripts} - this was originally part of the
        original specification, which wanted us to allow new players to see
        existing code and tweak it for better performance. We decided against
        this after we found this would be used at careers fairs to test
        candidates, as this would be unfair to the original authors of the
        scripts, and may lead to unfair perfomance comparisons.
        However, if the project were to be converted to more of a market than a
        performance tool, then this could then be integrated.
\end{itemize}
